---
title: "Linear model"
output: html_document
---
```{r setup, message=FALSE}
library(tidyverse)
library(p8105.datasets)
```


Load the NYC airbnb data
```{r dataload}
data(nyc_airbnb)
```

Look at the data/ do some cleaning
```{r clean}
nyc_airbnb <-
nyc_airbnb |>
mutate(
stars = review_scores_location / 2
) |>
rename(
borough = neighbourhood_group
) |>
filter(borough != "Staten Island") |>
select(price, stars, borough, room_type, neighbourhood)


```

Do regression
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

do some additional cleaning then refit.
```{r}
nyc_count <-
nyc_airbnb |>
count(borough)

nyc_airbnb <-
nyc_airbnb |>
mutate(
borough = fct_infreq(borough),
room_type = fct_infreq(room_type)
)

fit <- lm(price ~ stars + borough, data = nyc_airbnb)
```


look at `lm` stuff --- !Don't do this
```{r, message = FALSE, include=FALSE}
summary(fit)
names(summary(fit))
summary(fit)[["coefficients"]]
summary(fit)[["df"]]

fitted.values(fit)
```

Look at cleaner `lm` stuff

```{r}
fit |> 
  broom::tidy() |> 
  mutate(
    term = str_replace(term, "borought", "Borough: ")
  ) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)

```


## Diagnostics

Look at residuals.
```{r}
nyc_airbnb |> 
  modelr:: add_residuals(fit) |> 
  modelr:: add_predictions(fit) |>
  filter(resid < 1000) |> 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()

nyc_airbnb |> 
  modelr:: add_residuals(fit) |> 
  modelr:: add_predictions(fit) |>
  filter(resid < 1000) |> 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```


## Hypothesis testing
```{r}
fit |> 
  broom::tidy()   #give p-value
```

What about a categorical variable?

```{r}
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb) 
fit_alt |> broom::tidy()
fit_null = lm(price ~ stars + borough, data = nyc_airbnb) 
fit_null |> broom::tidy()

anova(fit_null, fit_alt)
```


## Interaction vs nested data
```{r}
fit_interactions =
  lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

fit_interactions |> 
  broom::tidy()
```

Let's just look at Brooklyn first.

```{r}
nyc_airbnb |> 
  filter(borough == "Brooklyn") |> 
  lm(price ~ stars + room_type, data = _) ##little underscore means the dataset go here
  broom::tidy()
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  lm(price ~ stars + room_type, data = _) ##little underscore means the dataset go here
  broom::tidy()
nyc_airbnb |> 
  filter(borough == "Bronx") |> 
  lm(price ~ stars + room_type, data = _) ##little underscore means the dataset go here
  broom::tidy()
nyc_airbnb |> 
  filter(borough == "Queens") |> 
  lm(price ~ stars + room_type, data = _) ##little underscore means the dataset go here
  broom::tidy()

```

Write a short function

```{r}
lm_airbnb = function(df) {
  
  lm(price ~ stars + room_type, data = df)
}

nyc_airbnb |> 
  filter(borough == "Queens") |> 
  lm_airbnb()
  broom::tidy()
```

Create a list of dataframes, and iterate to fit the model each time

```{r}
nested_lm_results = 
nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    fits = map(data, lm_airbnb),
    results = map(fits, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results)
```

Do some untidying.
```{r}
nested_lm_results |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  )
```


Use an *anonymous* fuction instead of `lm_airbnb`

```{r}
nested_lm_results = 
nyc_airbnb |> 
  nest(data = -borough) |> 
  mutate(
    fits = map(data, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(fits, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results)
```


Let's do an even more extreme example!!
```{r}
manhattan_analysis =
  nyc_airbnb |> 
  filter(
    borough == "Manhattan"
  ) |> 
  nest(data = -neighbourhood) |> 
  mutate(
    fits = map(data, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(fits, broom::tidy)
  ) |> 
  select(neighbourhood, results) |> 
  unnest(results)
```

Make a plot
```{r}
manhattan_analysis |> 
  filter(term == "stars") |> 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, estimate)
  ) |> 
  ggplot(aes(x = neighbourhood, y = estimate)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme_minimal()
``` 








